\documentclass{article}
\date{}
\usepackage{enumitem}
\setlist{nolistsep}
\usepackage{geometry}
 \geometry{
 a4paper,
 top=8mm,
 bottom=4mm,
 }
\usepackage{multicol}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=blue,
}
\usepackage{authblk}
\usepackage{fontawesome}
\usepackage{xcolor}
\begin{document}



\title{\LARGE}
\author{\LARGE \textbf{Jagadeesh \textcolor{violet}{Kotra}} }
\affil{\small \faStreetView \vspace{1mm} Hyderabad, India | \faPhone \vspace{1mm} \href{tel:+919392420045}{ +91 9392420045} |
\faEnvelope \vspace{1mm} \href{mailto:jagadeesh@stdin.top}{ jagadeesh@stdin.top}
 | \faGlobe \vspace{1mm} \href{https://stdin.top}{ stdin.top} \break
\faGithub \vspace{1mm} \href{https://github.com/jkotra}{jkotra} |
\faTwitter \vspace{1mm} \href{https://twitter.com/jagadeesh_kotra}{jagadeesh\_kotra} |
\faLinkedin \vspace{1mm} \href{https://www.linkedin.com/in/jagadeesh-kotra/}{jagadeesh-kotra}
}
\maketitle

\section{Introduction}

Enthusiastic and Motivated Software Developer
%seeking opportunity at \textbf{SomeCompany}
.Polyglot programmer proficient in problem solving and engineering. Active Open Source Contributor.

\section{Technical Skills}
\subsection{Programming Languages}
\begin{multicols}{3}
    \begin{itemize}
    	\item Java
        \item C / C++
        \item Python
        \item Rust
        \item JavaScript / TypeScript
        \item CUDA \& OpenCL
    \end{itemize}
\end{multicols}


\subsection{Frameworks}
\begin{multicols}{3}
    \begin{itemize}
    	\item Spring
    	\item Angular
        \item React Native
        \item GTK
        \item Pytorch
        \item Keras
    \end{itemize}
\end{multicols}


\subsection{Human Languages}
\begin{itemize}
    \item English - Professional Working Proficiency
    \item Telugu - Native Proficiency
\end{itemize}

\section{Projects}

\begin{itemize}
    \item \textbf{PDFUnlockr}
    \subitem
    \begin{itemize}
        \vspace{-0.25cm}
        \item Android Application built with React Native and \href{http://qpdf.sourceforge.net/}{qpdf}.
        \item uses RN's Native Modules to bridge between JavaScript and C++.
        \item Clean and clutter-free UI design. No limitation on decryption.
        \item Ability to process multiple files at a time AKA Bulk Processing.
        \item \href{https://play.google.com/store/apps/details?id=com.pdfunlockr}{Available on Google Play Store}.
        \vspace{0.35cm}
    \end{itemize}
    
    \item \textbf{OUResults}
    \subitem
    \begin{itemize}
        \vspace{-0.25cm}
        \item Android Application to view examination/semester results. Built with React Native.
        \item Utilizes publicly available endpoints to parse results from HTML.
        \item Persistence requests model to combat slow response during initial hours.
        \item \href{https://play.google.com/store/apps/details?id=com.ouresults}{Available on Google Play Store}.
        \vspace{0.35cm}
    \end{itemize}

    
    \item \textbf{eOVPN}
    \subitem
    \begin{itemize}
        \vspace{-0.25cm}
        \item Desktop GUI Application to Manage, Update and connect to OpenVPN Configurations. Made with \href{https://gtk.org/}{GTK}.
        \item Utilizes GNOME ecosystem of libraries -- GLib Gio, Gdk to seamlessly integrate with GNOME Desktop Environment.
        \item Open-source - \href{https://github.com/jkotra/eOVPN}{Available at Github}.
        \vspace{0.35cm}
    \end{itemize}
    

    \item \textbf{Nag}
	\subitem
	\begin{itemize}
		\vspace{-0.25cm}
		\item Nag enables you to set repeated reminders sent as notifications at customizable intervals. Built with React Native.
		\item adapts to MaterialYou Design principles introduced in Android 12.
        \item \href{https://play.google.com/store/apps/details?id=top.stdin.nag}{Available on Google Play Store}.
		\vspace{0.35cm}
\end{itemize}

\pagebreak

    \item \textbf{Algoticks}
    \subitem
    \begin{itemize}
        \vspace{-0.25cm}
        \item Algorithmic Trading simulator written in C. Optimized for one thing - SPEED. it can process up to 0.8 million \textit{lines / sec}.
        \item input data agnostic simulation.
        \item Easy to write algorithm template, supports custom callback modules (ex. logging)
        \item Open-source - \href{https://github.com/jkotra/algoticks/}{Available on Github}.
        \vspace{0.35cm}
    \end{itemize}
    
    \item \textbf{WPC}
    \subitem
    \begin{itemize}
        \vspace{-0.25cm}
        \item WPC - Wallpaper Changer is a cross-platform timer-based wallpaper changer. Written in Rust.
        \item It can automatically scrap wallpapers from different sources.
        \item Actively used and promoted by one of the popular internet wallpaper community.
        \item Open-source - \href{https://github.com/jkotra/wpc/}{Available on Github}.
        \vspace{0.35cm}
    \end{itemize}
    
    \item An up to date collection of all my projects is \href{https://stdin.top/portfolio/}{available on my blog}.                  
\end{itemize}

\section{Education}
Bachelor of Science (\textbf{B.sc}) M.P.CS \\
Sri Sai Degree \& PG Collage, Hyderabad \\
\emph{2018 - 2021}



\section{Miscellaneous}


 \subsection{Opensoure Contributions}
 \begin{multicols}{2}
 \begin{itemize}
     \item \href{https://gitlab.gnome.org/jkotra}{GNOME}
     \item \href{https://gitlab.freedesktop.org/jkotra}{freedesktop}
     \item \href{https://github.com/microsoft/LightGBM}{microsoft/LightGBM}
     \item \href{https://github.com/vapoursynth/vapoursynth}{Vapoursynth}
 \end{itemize}
\end{multicols}

\subsection{Recognitions}

\begin{itemize}
    \item \href{https://bugcrowd.com/netflix/hall-of-fame}{\textbf{Netflix} Hall of Fame}
\end{itemize}


\subsection{Certificates}

\begin{itemize}
    \item \href{https://www.coursera.org/account/accomplishments/certificate/E2FE7HNXWP8J}{Mathematics for Machine Learning: Linear Algebra}
    \item \href{https://www.coursera.org/account/accomplishments/certificate/QDPTGAQSXZNM}{Machine Learning with Python}
\end{itemize}

\end{document}